Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-05 paper/v1.0/sections/appendix_c.tex
Add content to Appendix c

Since the perturbation potential $V(\vb{r})$ is assumed to be formed by an ensemble of randomly distributed impurities, consider $N_{imp}$ identical impurities positioned at randomly distributed but fixed positions $\vb{r}_i$. Then scattering potential $V(\vb{r})$ is given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$
\begin{equation} \label{eq_c20}
  V(\vb{r}) \equiv
  \sum_{i=1}^{N_{imp}}
  \upsilon (\vb{r}-\vb{r}_i).
\end{equation}
Next we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of enerrgy such that the potential is zero on average. This model is characterized by \cite{akkermans10}
\begin{subequations}
\begin{equation} \label{eq_c21a}
  \expval{\upsilon(\vb{r})}_{imp} =0
\end{equation}
\begin{equation} \label{eq_c21b}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'})
\end{equation}
\end{subequations}
where $\expval{\cdot}_{imp}$ denoted the average over realizations of the impurity disorder. In addition, this model assume that $\upsilon (\vb{r}-\vb{r'})$ only dependes on the position difference $|\vb{r}-\vb{r'}|$ and it decays with a characteristic leangth $r_c$. Since this study considers the case where the waveleagth of radiation or scattering electrons is much faster than $r_c$, it is a good approximation to make two-point correlation function to be
\begin{equation} \label{eq_c22}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'})
\end{equation}
and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can model approximately the total scattering potential as
\begin{equation} \label{eq_c23}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
\end{equation}
Then we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
\begin{subequations}
\begin{align}
 V_{\vb{k'},\vb{k}} & =
 \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
 \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq_c24a} \\
 & =
 \sum_{i=1}^{N_{imp}}
 \int_{-\infty}^{\infty} dy\; \bigg[
 \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \\
 & \times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \bigg] \label{eq_c24b} \\
  & =
 \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
 e^{i(k'_y - k_y )y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}
\end{align}
\label{eqn:all-lines}
\end{subequations}

>>>>

Since the perturbation potential $V(\vb{r})$ is assumed to be formed by an ensemble of randomly distributed impurities, consider $N_{imp}$ identical impurities positioned at randomly distributed but fixed positions $\vb{r}_i$. Then scattering potential $V(\vb{r})$ is given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$
\begin{equation} \label{eq_c20}
  V(\vb{r}) \equiv
  \sum_{i=1}^{N_{imp}}
  \upsilon (\vb{r}-\vb{r}_i).
\end{equation}
Next we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of enerrgy such that the potential is zero on average. This model is characterized by \cite{akkermans10}
\begin{subequations}
\begin{equation} \label{eq_c21a}
  \expval{\upsilon(\vb{r})}_{imp} =0
\end{equation}
\begin{equation} \label{eq_c21b}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'})
\end{equation}
\end{subequations}
where $\expval{\cdot}_{imp}$ denoted the average over realizations of the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$. In addition, this model assume that $\upsilon (\vb{r}-\vb{r'})$ only dependes on the position difference $|\vb{r}-\vb{r'}|$ and it decays with a characteristic leangth $r_c$. Since this study considers the case where the waveleagth of radiation or scattering electrons is much faster than $r_c$, it is a good approximation to make two-point correlation function to be
\begin{equation} \label{eq_c22}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'})
\end{equation}
where $\Upsilon_{imp}$ is stregth of the delta potential and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can model approximately the total scattering potential as
\begin{equation} \label{eq_c23}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
\end{equation}
Then we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
\begin{subequations} \label{eq_24}
\begin{align}
 V_{\vb{k'},\vb{k}} & =
 \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
 \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq_c24a} \\
 & =
 \sum_{i=1}^{N_{imp}}
 \int_{-\infty}^{\infty} dy\; \bigg[
 \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \\
 & \times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \bigg] \label{eq_c24b} \\
  & =
 \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
 e^{i(k'_y - k_y )y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}.
\end{align}
\end{subequations}
Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs and assuming the total ncumber of scatterers $N_{imp}$ is macroscopically large, we can derive
\begin{subequations} \label{eq_c25}
  \begin{align}
    V_{\vb{k'},\vb{k}}
    & =
    V_{k'_x,k_x}
    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty} dy_i\;
    e^{i\qty({k'}_y - k_y)y_i} \label{eq_c25a} \\
    & =
    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y), \label{eq_c25a}
  \end{align}
\end{subequations}
where
\begin{equation} \label{eq_c26}
  V_{{k'}_x,k_x} \equiv
  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x}.
\end{equation}
is a constant value for every $i$ impurity and $\eta_{imp}$ is number of impurities in a unit area. It is important to notice that $\ket{k_x} = e^{-ik_xx}$.

Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25}) on Eq.~(\ref{eq_c19}), we obtain
\begin{equation} \label{eq_c27}
  \begin{aligned}
    Q & =
    \sum_{k_x}\sum_{{k'}_x}
    {\eta_{imp} V_{{k'}_x,k_x}}
    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} dk_y d{k'}_y \;
    \delta({k'}_y - k_y)
    \\
    & \times
    \sqrt{L_x}
    \exp(
      i{k'}_y  \qty[d\sin(\omega t) + {y'}_0]
    )
    \tilde{\chi}_{n_{\beta}}\qty({k'}_y -b\cos(\omega t))
    \\
    & \times
    \sqrt{L_x}
    \exp(
      -ik_y  \qty[d\sin(\omega t) + y_0]
    )
    \tilde{\chi}_{n_{\alpha}}\qty(k_y -b\cos(\omega t)),
  \end{aligned}
\end{equation}
and this can simplify as
and this can re-write as
\begin{equation} \label{eq_c28}
  \begin{aligned}
    Q =
    \sum_{k_x}\sum_{{k'}_x}
    {\eta_{imp} L_x V_{{k'}_x,k_x}} I,
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_c29}
  \begin{aligned}
    I \equiv
    \int_{-\infty}^{\infty} dk_y \;
    \tilde{\chi}_{n_{\beta}}\qty(k_y -g\cos(\omega t)) &
    \tilde{\chi}_{n_{\alpha}}\qty(k_y -g\cos(\omega t)) \\
    & \times
    \exp(
      -ik_y  \qty[y_0 - {y'}_0  ]
    ).
  \end{aligned}
\end{equation}
